In order to prepare for a succesfull entry to the market, we have created a list of commercial challenges. In the sections below we will elaborate the most important challenges, but the complete list of challenges is illustrated in appendix \ref{CommercialChallenges}.

\subsubsection{Gaining market shares}
In a market with strong and well-established competitors, it is difficult for a new company to gain a market position. Companies such as Lauritz.com, Bruun Rasmussen and DBA have existed for several years, and have a strong position in the mind of the consumers. The challenge is to convince the consumers to use Artion instead of the platforms they are used to.\\
\forceindent With our analysis of the competitors business models in appendix \ref{BusinessModels}, we are aware of entry barriers in the market. We believe we have the needed innovative value proposition in order to penetrate the market.

\subsubsection{Deadlocks}
The second challenge is to eliminate the possibility for a deadlock. The whole foundation for the app is based on the presence of both buyers and sellers. If only buyers are present, the application has no purpose. The same applies for the other way around. The sellers need buyers to purchase the products, and the buyers need sellers to provide products. We need to attract both parties before launching the application, in order to establish this synergy effect. 

\subsubsection{Meeting the needs of each segment}
As described in section \ref{Segment}, we identify three segments for Artion. Confronting all segments at the same time might be very difficult in terms of marketing and strategy. Therefore, we have to develop separate marketing strategies for each segment in order to accommodate their diverse needs. 