Following section introduces the unique features of our application. 

\section*{Frame recognising camera}
The frame recognising camera is one of the essential features that makes our application unique. When a user creates an auction in the application he must use the camera built-in function that recognises the frame of the painting and only captures what is within the frame. In this way we ensure a consistent presentation of all auctions. See appendix \ref{CreateAuctionSketch}.

\section*{Simplicity}
One of the reasons for us to develop this app is that the existing platforms at the current market are not simple and easy to use. Lauritz.com provides a quite easy and simple application, but they manage all of the auctions including valuation of the products, creation of the auctions, picturing of the products, storing of the products in showrooms and distribution of the products after hammering themselves. We found that the application Lauritz.com provides is simple and easy to use, but the associated processes are very difficult for both the seller and the buyer.

\section*{Safe transactions}
With inspiration from services like AirBnB and Uber, we introduce the transaction-confirmation feature. All transactions and payments are managed by the application. When an auction has ended, the amount of money payed by the buyer is locked in the system. The seller will be notified when the buyer has payed for the product, but the seller will not receive any money before the painting is received by the buyer. We have implemented a user interface that enables the buyer and seller to confirm that the exchange of the painting has taken place, whereafter the seller receives the money.  