To secure anchorage of Artion, various strategic initiatives and general assumptions about the market will be presented in the following section. The choice of strategies reflects patterns of how Artion can leverage on its core competences to secure competitive advantages in the market.
\\\\
In strategic typology, Artion can be seen as a combination of the prospector and the analyser. Artion seeks to leverage on the opportunities of the current market situations of art, as we want to improve the time to market by connecting the dots. This could potentially create a new and more consistent market. However, one could also argue that the idea of Artion builds on existing concepts and therefore is a more analytic and sustaining approach.
\\\\
Artion faces two user segments. Artists, gallerist and private art-distributers which can be categorised as the sellers. The other segment is buyers, which is everyone with an interest in art. The sellers create a supply and the buyers create the demand.

One of the key strategies to establish value creation is by using wisdom of the crowd. By creating a community Artion can leverage on the collective intelligence from artists, gallerists and private art-distributors sharing their ideas. As Artion has various users with different agendas we see our users of the community as mobs who contribute as individual specialist but has relatively homogeneous interest because of an artist general interest in getting inspired by others in the community. 
\\\\
To recruit members various strategies can be implemented. As we start from point zero our approach is to ask for volunteers which regarding to AnHai Doan & co is the most popular solution. One approach is to screen the market for potential users of the community. This process can both take place online by searching groups & communities for art in social media. But also by promoting physically at vernissages and exhibitions. Another approach is by hosting events where people can try-out the app. At the events, we will be offering free setup and guidance of how the platform works in order to establish a relationship with our users. A good reputation is important when entering an already established market. A third way to reach our potential users is through social media and sponsored partnerships but cost follow this approach and therefore it’s a limited resource. 

In this context user interface becomes very important. As AnHai Doan & co formulate it: "The user interface should make it easy for users to contribute. This is highly non-trivial." The user interface will be described more detailed in the section about HCI, but its important to state that the interface is closely connected to the recruitment of users.
\\\\
Together these assumptions can be formed into the following overall strategy:

Artion wants to secure the sellers by not only creating a platform to distribute their art, but also to create a community where indirect benefits of getting inspired and sharing art can be redeemed. Value creation for Artion is created by user activity and therefore it’s important to prioritise the users first. A relationship to our users is created through good reputation, an appealing user interface and good user experience. 
