\subsubsection*{Persona 1: Artist}

\begin{itemize}
    \item Personal information: Kjeld Andersen, age 34, Artist. Educated artist at 'Det Jyske Kunstakademi'. Works as a self-employed artist. Currently lives in Copenhagen Oe., together with his wife and two years old daughter.
    \item Needs: Kjeld could becoming a future user of our applications, as he want to scale the amount of potential buyers of his arts
    \item Motivation: The amount of users of our platform. The cheap fees and secure payment.
    \item Challenges: The current challenges that Kjeld faces, is that he doesn't hit many buyers, then he takes his art to the local vernissage. We can support Kjeld, by aiming a lot of direct and indirect buyers with our online platform.
    \item Buying role: He is the seller on this trading platform
\end{itemize}

\subsubsection{Persona 2: Gallerist}
\begin{itemize}
    \item Personal information: Mogens Hermann, age 53, Gallerist. Educated Master of Fine Arts at "Det kongelige danske kunstakademi - billedkunstskolerne". Works at his own gallery. Currently lives in Copenhagen N., but have gained a lot of knowledge with his work in Los Angeles
    \item Needs: As Persona 1, he wants a platform, where he can hit a large amount of buyers, without any associations with DBA, Facebook or something else. 
    \item Motivation: Large number of potential buyers. Cheap fees. 
    \item Challenges: Doesn't hit many buyers. Artion ensures future increasing
    \item Buying role: He is the seller on this trading platform.
\end{itemize}

\subsubsection{Persona 3: Private People}
\begin{itemize}
    \item Personal information: Emma Jensen, age 24, art enthusiast. Educated pedagogue at 'Campus Carlsberg'. Works as a pedagogue at 'Skolen ved Søerne'. Currently lives in Amager with her boyfriend.
    \item Needs: She wants an application exclusively for paintings.
    \item Motivation: Easy access. Cheap starting cost. Possible bargains
    \item  Challenges: Many opportunities for trading platforms. But not one specific for painting.
    \item Buying role: She is the buyer on this trading platform.
\end{itemize}