This chapter provides a detailed depiction of the value adding activities being performed by our application. Following sections will explain the activities we consider the most value-adding. The complete range of activities for respectively the seller and the buyer is illustrated as service blueprints in appendix \ref{ServiceBlueprint}. The key innovative feature of our application is the combination of the following three activities. 

\section{Display of auctions}
\label{DisplayOfAuctions}
The first essential value adding activity performed by the application, is the display of auctions. The first step in figure \ref{ServiceBlueprintBuyer} is the customer opening the application. This action performed by the user initiates the application to expose a list of auctions. This list is presented as a grid showing large consistent pictures of the various paintings, including date and time of expiration and price. The frame recognising camera feature ensures a consistent presentation of all pictures in the grid. The grid is divided into two columns and has infinite scroll. The grid displaying all auctions in the application is illustrated in figure \ref{AuctionsGrid}.

\section{Easy and short time to market}
One of the most value adding activities performed by the application is the quick and easy way of creating an auction. The second step in figure \ref{ServiceBlueprintSeller} is the seller pressing the + (create advertisement) button. This action performed by the seller initiates the application to open the frame recognising camera. Once the picture is taken, the seller has to provide the information associated with the painting, and then the auction is ready for publishing. The process of creating an auction is illustrated in figure \ref{CreateAuction}. 

\section{Safe transactions}
Another essential value adding activity is the handling of payments. When an auction has ended, the buyer has to pay the hammer price via the integrated payment module. The payment is then locked in the system and only proceeds to the seller when both parties have confirmed the hand-over via the confirmation interface, provided by the application. This concept is inspired by AirBnB\footnote{https://www.airbnb.dk}. The confirmation interface is illustrated in the horizontal prototype in appendix \ref{HorizontalPrototype}.